The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-12-31 paper.tex
Revised section on repeater networks.

We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons, and in Section \ref{sec:encoding} with a description of some commonly used qubit encodings. Any unitary transformation acting on the spatial label of single photons can be efficiently decomposed into a network of beamsplitters and phase-shifters. We discuss this, and an extension to handle additional internal states, in Section \ref{sec:decomp}. For applying any linear optical circuit, one needs an accurate description of its unitary representation. A full quantum tomography is costly and time-consuming. Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction}. In Section \ref{sec:state}, we recap the experimental breakthroughs in state preparation of single photons, and some entangled quantum states. This is followed by advances in time-bin based architecture for linear optical networks, and photodectors in Sections \ref{sec:timebins} and \ref{sec:detector} respectively. Last, but not least, we review applications for linear optical interferometry in LOQC, {\sc bosonsampling}, \sihui{ quantum metrology, and quantum repeat networks}.

@@

Without the use of repeaters, it has been shown that the rate transmission of a channel with loss without entanglement assistance has a linear fallout \cite{bib:TGW14}, and its bound is known as the Takeoka-Guha-Wilde (TGW) bound. The minimal resources required to exceed the TGW bound is a subject of active research, and so far it has been shown that the performance of the repeater schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al. \cite{bib:Sinclair14} are able to exceed the TGW bound. Other benchmarking tools have also been used to analyze many of these repeater schemes in detail \cite{bib:Muralidhara16}. More details about repeaters and long-distance quantum communication can be found in review papers on these subjects \cite{bib:Kimble08,bib:Sangouard11, bib:MATN15}.

>>>>

We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons, and in Section \ref{sec:encoding} with a description of some commonly used qubit encodings. Any unitary transformation acting on the spatial label of single photons can be efficiently decomposed into a network of beamsplitters and phase-shifters. We discuss this, and an extension to handle additional internal states, in Section \ref{sec:decomp}. For applying any linear optical circuit, one needs an accurate description of its unitary representation. A full quantum tomography is costly and time-consuming. Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction}. In Section \ref{sec:state}, we recap the experimental breakthroughs in state preparation of single photons, and some entangled quantum states. This is followed by advances in time-bin based architecture for linear optical networks, and photodectors in Sections \ref{sec:timebins} and \ref{sec:detector} respectively. Last, but not least, we review applications for linear optical interferometry in LOQC, {\sc bosonsampling}, \sihui{ quantum metrology, and quantum repeater networks}.

@@

Without the use of repeaters, it has been shown that the rate transmission of a channel with loss without entanglement assistance has a linear fallout \cite{bib:TGW14}, and its bound is known as the Takeoka-Guha-Wilde (TGW) bound. The minimal resources required to exceed the TGW bound is a subject of active research, and so far it has been shown that the performance of the repeater schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al. \cite{bib:Sinclair14} are able to exceed the TGW bound. Other benchmarking tools have also been used to analyze many of these repeater schemes in detail \cite{bib:Muralidhara16}. In terms of implementation, the greatest distance that a quantum state has been teleported to-date is 1400 km \cite{bib:Ren17}, and is demonstrated between an earth-based source with a detection unit on a satellite in space. This is a culmination of many decades of research from many groups in extending this distance. If it could be made to work with other basic units of quantum repeater networks that have been implemented \cite{bib:Kimble08,bib:Sangouard11, bib:MATN15}, a large-scale, long-distance repeater network could soon be possible.
